Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

Given an $(n_1, n_2, ..., n_k)$-input $\set{R_1, R_2, ..., R_k}$, we execute the algorithm by traversing a root-to-leaf path in $\T$. In general, at an internal node with the instruction $(i, \lambda, \side; i', \lambda', \side')$, we first identify
\myitems{
    \item $r$ as the rectangle with ID $\lambda$ in $R_i$;
    \item $r'$ as the rectangle with ID $\lambda'$ in $R_{i'}$.
}
Then, we compare $\side(r)$ to $\side'(r')$ (e.g., if $\side = \xright$ and $\side' = \ybot$, then the comparison is between $\xright(r)$ to $\ybot(r')$). We branch to
\myitems{
    \item the left child if $\side(r) < \side'(r')$;
    \item the middle child if $\side(r) = \side'(r')$;
    \item the right child if $\side(r) > \side'(r')$.
}
At a leaf, we look at its associated result and, for each $(\lambda_1, \lambda_2, ..., \lambda_k)$ in that result, output $(r_1, r_2, ..., r_k)$ where $r_i$ ($i \in [k]$) is the rectangle with ID $\lambda_i$ in $R_i$. The algorithm must produce the correct output on all $(n_1, n_2, ..., n_k)$-inputs. Its {\em worst-case cost} is the height of $\T$.

@@

When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a containment query on $\T$ to find all the intervals in $S_\ell$ that are contained by $[z_1, z_2]$; if $K_h$ is the number of such intervals, this retrieval takes $O(\log n + K_h)$ time. For each retrieved interval $[x_1, x_2]$, we also obtain its host rectangle $r$ (stored along with $[x_1, x_2]$ in $\T$). As can be verified shortly, $h$ is the lowest segment in $H$ that crosses $r$; we therefore output $(r, h)$. After that, $r$ is marked as inactive, and accordingly, its x-range $[x_1, x_2]$ is deleted from $T$ in $O(\log n)$ time. As $r$ will remain inactive in the rest of the execution, its x-range will not be retrieved again by another containment query in the future. This implies that $h$ is indeed the lowest segment in $H$ crossing $r$.

>>>>

Given an $(n_1, n_2, ..., n_k)$-input $\set{R_1, R_2, ..., R_k}$, we execute the algorithm by traversing a root-to-leaf path in $\T$. In general, at an internal node with the instruction $(i, \lambda, \side; i', \lambda', \side')$, we first identify
\myitems{
    \item $r$ as the rectangle with ID $\lambda$ in $R_i$;
    \item $r'$ as the rectangle with ID $\lambda'$ in $R_{i'}$.
}
Then, we compare $\side(r)$ to $\side'(r')$ (e.g., if $\side = \xright$ and $\side' = \ybot$, then the comparison is between $\xright(r)$ to $\ybot(r')$). We branch to
\myitems{
    \item the left child if $\side(r) < \side'(r')$;
    \item the middle child if $\side(r) = \side'(r')$;
    \item the right child if $\side(r) > \side'(r')$.
}
At a leaf, we look at its associated result and, for each $(\lambda_1, \lambda_2, ..., \lambda_k)$ in that result, output $(r_1, r_2, ..., r_k)$ where $r_i$ ($i \in [k]$) is the rectangle with ID $\lambda_i$ in $R_i$. The algorithm is required to produce the correct output on all $(n_1, n_2, ..., n_k)$-inputs. Its {\em worst-case cost} is the height of $\T$.

@@

When $\ell$ hits a horizontal segment $h = [z_1, z_2] \times y$ of $P$, perform a containment query on $\T$ to find all the intervals in $S_\ell$ that are contained by $[z_1, z_2]$; if $K_h$ is the number of such intervals, this retrieval takes $O(\log n + K_h)$ time. For each retrieved interval $[x_1, x_2]$, we also obtain its host rectangle $r$ (stored along with $[x_1, x_2]$ in $\T$). As can be verified shortly, $h$ is the lowest segment in $H$ that crosses $r$; we therefore output $(r, h)$. After that, $r$ is marked as inactive, and accordingly, its x-range $[x_1, x_2]$ is deleted from $\T$ in $O(\log n)$ time. As $r$ will remain inactive in the rest of the execution, its x-range will not be retrieved again by another containment query in the future. This implies that $h$ is indeed the lowest segment in $H$ crossing $r$.
